### 2018-09-09 ICRA19/covControl.tex
changed section name.. we need to read this paper carefully

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Covariance control}
\label{sec:covControl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\linewidth]{SquareFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a square boundary wall allows limited control of the shape of the swarm, as a function of swarm area $A$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for five values of $A$.  %The locus morphs from a square to a circle as $A$ increases.  The covariance ellipse for each $A$ is shown with a dashed line.
 Center shows two corresponding arrangements of kilobots. % At right is $\bar{x}(A), \sigma_{xy}(A), \sigma_x^2(A),$ and $\rho(A)$ for a range of $\beta$ values. See online interactive demonstration at \cite{Zhao2016mathematicaSquare}.
 }
\label{fig:SquareFill}
\end{center}
\end{figure*} 
\begin{figure*}[!htb]
\begin{center}
\vspace{-1em}
\includegraphics[width=\linewidth]{CircleFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a circular boundary wall allows limited control of the shape of the swarm, as a function of the fill level $h$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for four values of $h$. %The locus of possible mean positions are concentric circles. %See online interactive demonstration at \cite{Zhao2016mathematica}.
}  
\label{fig:CircleFill}
\end{center}
\vspace{-1em}
\end{figure*} 
Covariance control as well as mean position and variance control is needed when the swarm is moving through narrow passageways. This section discusses ideas to control covariance of the swarm using boundaries.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shape  Control using Rigid Boundaries}
\label{sec:covControl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\linewidth]{SquareFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a square boundary wall allows limited control of the shape of the swarm, as a function of swarm area $A$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for five values of $A$.  %The locus morphs from a square to a circle as $A$ increases.  The covariance ellipse for each $A$ is shown with a dashed line.
 Center shows two corresponding arrangements of kilobots. % At right is $\bar{x}(A), \sigma_{xy}(A), \sigma_x^2(A),$ and $\rho(A)$ for a range of $\beta$ values. See online interactive demonstration at \cite{Zhao2016mathematicaSquare}.
 }
\label{fig:SquareFill}
\end{center}
\end{figure*} 
\begin{figure*}[!htb]
\begin{center}
\vspace{-1em}
\includegraphics[width=\linewidth]{CircleFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a circular boundary wall allows limited control of the shape of the swarm, as a function of the fill level $h$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for four values of $h$. %The locus of possible mean positions are concentric circles. %See online interactive demonstration at \cite{Zhao2016mathematica}.
}  
\label{fig:CircleFill}
\end{center}
\vspace{-1em}
\end{figure*} 
Shape control using angle of repose only considers the particles that pile up on the object, but most of the particles pass by.
 This section instead focuses on shape control of the entire group when all the particles are pushed against rigid boundaries, starting by examining analytically all possible configurations in two canonical configuration spaces, and then examining the effect of boundary layer friction.
